Pre-processing high frequency animal tracking data

### 2020-08-28 02_filtering_data.Rmd
add scale landscape
compare speed

@@

```{r scale_landscape}
# a function to scale the landscape
do_scale_landscape <- function(land_, scale_factor) {
  bounds <- c(0, 1, 0, 1)
  bounds <- bounds * scale_factor
  raster::extent(land_) <- bounds
  return(land_)
}
```

@@

  # make speed results
  speed_res <- data.table(type = c("reference", "outliers", "cleaned"),
                          speed = c(speed, error_speed, clean_speed))
  results <- list(land_props = land_props,
                  speed_res = speed_res)

  return(land_props)
}, 
param_c$p_outlier, 
param_c$ext_outlier,
param_c$land_scale,
SIMPLIFY = FALSE)
```

```{r}
# get bound list
sim_data <- rbindlist(sim_data)
# get differences between outliers and cleaned wrt ref
#sim_data[, `:=`(d_cleaned = abs(cleaned - reference),
 #               d_outliers = abs(outliers - reference))]

sim_data_long <- copy(sim_data)

sim_data_long <- melt(sim_data_long, 
                      id.vars = c("land_values", "ext_outlier", 
                                  "p_outlier", "scale"))

ggplot(sim_data_long)+
  geom_boxplot(aes(x = factor(land_values),
                   y = value,
                   col = variable))+
  facet_grid(scale ~ ext_outlier, scales = "free")
```

>>>>

# strings
library(glue)

@@

@@

  # make speed results
  speed_res <- data.table(type = c("reference", "outliers", "cleaned"),
                          speed_mean = unlist(lapply(list(speed, 
                                                          error_speed, 
                                                          clean_speed),
                                                     mean, na.rm = TRUE)),
                          speed_sd = unlist(lapply(list(speed, 
                                                          error_speed, 
                                                          clean_speed),
                                                     sd, na.rm = TRUE)),
                          scale = scale,
                          p_outlier = p_outlier,
                          ext_outlier = ext_outlier
                          )
  results <- list(land_props = land_props,
                  speed_res = speed_res)

  return(results)
}, 
param_c$p_outlier, 
param_c$ext_outlier,
param_c$land_scale,
SIMPLIFY = FALSE)
```

```{r outlier_removal_land_prop}
# get bound list
land_prop_data <- rbindlist(lapply(sim_data, function(l) { l$land_props }))
# get differences between outliers and cleaned wrt ref
#land_prop_data[, `:=`(d_cleaned = abs(cleaned - reference),
 #               d_outliers = abs(outliers - reference))]

land_prop_data_long <- copy(land_prop_data)

land_prop_data_long <- melt(land_prop_data_long, 
                            id.vars = c("land_values", "ext_outlier", 
                                        "p_outlier", "scale"))

ggplot(land_prop_data_long)+
  # geom_boxplot(aes(x = factor(land_values),
  #                  y = value,
  #                  group = interaction(variable, scale, land_values),
  #                  fill = variable))+
  geom_line(aes(x = (land_values),
                y = value,
                group = interaction(variable, scale),
                col = variable,
                lty = factor(scale)),
            stat = "summary")+
  geom_point(aes(x = (land_values),
                 y = value,
                 group = interaction(variable, scale),
                 col = variable,
                 shape = factor(scale)),
             size = 2,
             stat = "summary")+
  facet_grid( ~ ext_outlier, 
              scales = "free_y",
              labeller = label_both)+
  theme_classic()+
  theme(strip.background = element_rect(fill = "grey90",
                                        colour = NA))
```

```{r outlier_removal_speed}
# get speed data
speed_data <- rbindlist(lapply(sim_data, function(l) { l$speed_res }))

# melt to
speed_data_long <- copy(speed_data)

speed_data_long <- melt(speed_data_long, 
                            id.vars = c("ext_outlier", "type",
                                        "p_outlier", "scale"))

ggplot(speed_data_long)+
  # geom_boxplot(aes(x = factor(land_values),
  #                  y = value,
  #                  group = interaction(variable, scale, land_values),
  #                  fill = variable))+
  geom_boxplot(aes(x = factor(ext_outlier),
                   y = value,
                   col = type))+
  facet_grid(~ variable, 
              scales = "free_y",
              labeller = label_both)+
  theme_classic()+
  theme(strip.background = element_rect(fill = "grey90",
                                        colour = NA))
```
